%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Long Professional Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{geometry}
\newsectionwidth{0pt} % Stops section indenting
\geometry{left=10mm,
 right=10mm,
 top=5mm,
 bottom=5mm}

\begin{document}

%----------------------------------------------------------------------------------------
%	YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------

\name{Narendra Kumar Soni\\ \\} % Your name at the top

% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket

\address{\#8-43, Blk-20, Woodlands Crescent\\Northoaks, Singapore, 738081 \\ +65 8399 4009 \\ narendrasoni2@gmail.com } % Your address 1

%\address{ www.webexpressive.com \\ https://sg.linkedin.com/in/narendrakumarsoni  \\  https://github.com/narendrasoni1989 \\http://stackoverflow.com/users/2161130/narendrasoni  } % Your address 2

\address{ www.webexpressive.com \\ https://sg.linkedin.com/in/narendrakumarsoni   \\http://stackoverflow.com/users/2161130/narendrasoni  \\https://github.com/narendrasoni1989 } % Your address 2


%----------------------------------------------------------------------------------------

\begin{resume}
\moveleft\hoffset\vbox{\hrule width 200mm height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
\vspace{-0.2in} % Some whitespace between sections
\section{\centerline{OBJECTIVE}}

\vspace{6pt} % Gap between title and text

Passionate software engineer who believes in continuous learning, utilising his software development skills to develop and support mission critical applications.\\ 

\vspace{-0.25in} % Some whitespace between sections
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{EDUCATION}} 

\vspace{6pt} % Gap between title and text

{\sl Post Graduate Diploma}, System Analysis \\ 
National University Of Singapore, Singapore \hfill June 2014 \\ 
CAP 4.13 
 
{\sl Bachelor of Engineering}, Information Technology \\ 
Chhattisgarh Swami Vivekanand Technical University, Bhilai, India   \hfill May 2011 \\
CPI : 8.5
%----------------------------------------------------------------------------------------
 
\vspace{-0.1in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{PROFESSIONAL EXPERIENCE}} 

\vspace{3pt} % Gap between title and text



{\sl J. Walter Thompson, Singapore} \hfill August 2016 -- Present \\
Full Stack Developer, DevOPs  \hfill
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Orchestrating ideas of creative teams in the form of digital contents like web pages and mobile apps.
\item Involved in analysis, designing, development(front end and back end), deployment, testing, maintenance and support of web applications.
\item Configure/maintain secure, robust, autoscale, high availability infrastructure for new and existing applications in AWS.
\item Linux, Apache, Amazon Web Services administration of production/staging/testing environments.
\item Technology Stack - jQuery, AngularJs, Java, PHP, Laravel, NodeJS, Gulp, MySQL, MongoDB, Oracle, Amazon Web Services, Adobe AEM 6.1, Git, Spring, Hibernate, MySql, DynamoDB
\item Key Projects include changiairport.com, one.changiairport.com, Changi Millionaire 
\end{itemize}

{\sl Hello Technology Pte. Ltd., Singapore} \hfill September 2014 -- August 2016 \\
Software Engineer \hfill 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Involved in design, development, testing, deployment and maintenance of Hello Tech's flagship project such as Hello Marketing and Tok-Tok Enterprise Messenger.
\item Development, design, maintenance, support and complete ownership of EMT Client(End to End Mobile Testing), an Android application to ensure zero downtime for OTP and Fund transfer SMS services for Banking Clients.
\item Design, development, maintenance and support of Tok-Tok Server and Tok-Tok Android Client. Tok-Tok is an enterprise chatting application. Tok-Tok server comes with contact management portal  for administration of users and conversations from various organisations. Tok-Tok is used by clients such as Singapore Airlines, TPJC, ACJC and many other schools in Singapore.
\item Technology Stack - Java,, MySql, MongoDB, GWT, Android, Spring, Hibernate, Apache Tomcat, Hazelcast, Sencha
\end{itemize}

{\sl CrimsonLogic Pte. Ltd., Singapore} \hfill October 2013 -- August 2014 \\
Software Engineer  \hfill
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Developed business modules in  Trade facilitation, e-government  projects (Enterprise Web, Native Mobile Application).
\item Involved in analysis, designing, development and testing of a complete module.
\item Technology Stack - HTML, Javascript, jQuery, JSF, Spring, Hibernate, Android
\end{itemize}
 

{\sl Tata Consultancy Services Ltd., Bengaluru, KA, India} \hfill December 2011 -- January 2013 \\
Assistant System Engineer \hfill
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Contributed in some of the highly challenging projects and  assignments such as  Loan Origination System, Capital Market, Assure, MBT-
KMP, Dashboard for one of the US based banking and finance giant by working as an enterprise java application developer.
\item Demonstrated projects and handled communication with clients during the project delivery phase.
\end{itemize}

%----------------------------------------------------------------------------------------

\vspace{-0.1in} % Some whitespace between sections
%----------------------------------------------------------------------------------------
%	CERTIFICATIONS
%----------------------------------------------------------------------------------------
\section{\centerline{CERTIFICATIONS}}
\vspace{15pt} % Gap between title and text
\begin{itemize} \itemsep -2pt % Reduce space between items
\item{Oracle Certified Professional Java Programmer (OCPJP 1.6)}
\end{itemize}

%\vspace{8pt} % Gap between title and text

%----------------------------------------------------------------------------------------

\vspace{-0.1in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{TECHNICAL SKILLS}}

\vspace{5pt} % Gap between title and text

{\sl Programming Language} \hfill \\
JAVA, HTML5, Javascript, Shell Scripting, Node.js, Android

{\sl Framework} \hfill \\
Struts, Spring, Play Framework, JSF, Hibernate, GWT, ExpressJS, AngularJS, D3.js, Twitter Bootstrap, jQuery, Quartz, LDAP

{\sl Database} \hfill \\
Oracle, MySQL, MongoDB 

{\sl Cloud} \hfill \\
Amazon Web Services, Google Cloud, Digital Ocean

{\sl Webserver} \hfill \\
Apache Tomcat, Weblogic, JBoss

{\sl Tools} \hfill \\
Ant, Maven, Grunt, Mocha

{\sl Continuous Integration} \hfill \\
Travis CI

{\sl Other skills} \hfill \\
Knowledge of Design patterns, REST API designing, Micro Services, Scalable Architectures, Algorithms and Data Structures, Test Driven Development, Deployment Practices, Search Engine Optimisation, XML, JSON, Docker
%----------------------------------------------------------------------------------------



%\vspace{0.1in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	MEMBERSHIPS SECTION
%----------------------------------------------------------------------------------------

%\section{\centerline{MEMBERSHIPS}} 

%\vspace{-5pt} % Reduce space between section title and contents

%\begin{center}
%Alumni representative, Industrial speaker at Institute of Systems Science, National University of Singapore \\
%Vice President of Education, Competent Communicator at Toastmasters International Toa Payoh Central CC, Singapore
%\end{center}

%----------------------------------------------------------------------------------------

%\vspace{0.01in} % Some whitespace between sections
\vspace{-0.1in}
%----------------------------------------------------------------------------------------
%	HONORS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{AWARDS \& RECOGNITIONS}} 

\vspace{-5pt} % Reduce space between section title and contents

\begin{center}
Awarded Star performer of learners group at Initial learning program by Tata Consultancy  Services ltd., Ahmedabad \\
Winner, Humorous Speech Contest, Runner up, Table topics contest at TPCC Toast Masters International Club, Singapore \\
Finalist Javawise 2009, IIT Kharagpur, WB, India
\end{center}

%----------------------------------------------------------------------------------------

%\vspace{0.01in} % Some whitespace between sections
\vspace{-0.19in}
%----------------------------------------------------------------------------------------
%	EXTRA CURRICULAR ACTIVITIES
%----------------------------------------------------------------------------------------

\section{\centerline{EXTRA-CURRICULAR ACTIVITIES}} 

\vspace{8pt} % Gap between title and text
{\sl Toa Payoh Central Toastmasters club, Singapore} \hfill November 2014 -- Present \\
Vice President of Education  \hfill 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Active member, playing a key role in running chapter meetings at Toa Payoh Central Toastmasters club, Singapore.
\end{itemize}

{\sl NUS iCARE} \hfill May 2013 -- December 2013 \\
Core committee member \hfill 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item A committee devoted to welcome, help new international students settle down in Singapore and get familiar with NUS. 
\item Project Director for Deepavali Celebration, Welfare and training coordinator. 
\item Responsibilities include organize events, volunteer recruitment and engagement, plan and coordinate training session for i.CARE core 
team members, organize recreation sessions.
\end{itemize}

{\sl FOSSASIA, Singapore} \hfill March 2016  \\
Volunteer, Moderator \hfill 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item FOSSASIA is the premier Free and Open Source technology event in Asia for developers, start-ups, and contributors. Projects at FOSSASIA range from open hardware, to design, graphics and software.
\end{itemize}

{\sl Himalayan Range Trekking }\\
Participant \hfill 
\begin{itemize} \itemsep -2pt
\item I constantly challenge myself by participating in high altitude trekking and adventure sports.
\item Participated in Trekking programs at Solang Valley, Manali, HP, India(13200 ft) and Kuari Pass, UK, India(12800 ft). 
\item Experience of rock climbing, river crossing, monkey crawling, river rafting, bungee jumping, Zip Line
\item Next in bucket list are Kilimanjaro, Tanzania, Africa and Chadar Winter trek, Ladakh, India. 
\end{itemize}

%----------------------------------------------------------------------------------------

%\vspace{0.1in} % Some whitespace between sections
\vspace{-0.12in} 
%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{INTERESTS}} 

\vspace{-5pt} % Reduce space between section title and contents

\begin{center}
Rollerblading, Public Speaking, Travelling, Hiking, Adventure Sports
\end{center} 

%----------------------------------------------------------------------------------------

\end{resume} 
\end{document}